\boldmath Heavy resonances at energy frontier colliders

### 2019-02-01 paper.tex
Updates from ShareLaTeX

%%%%%%%%%
\subsection{Simulation of the detector response}
\label{subsec:detparam}

@@

The detector response has been simulated via the Delphes software package~\cite{deFavereau:2013fsa}. For the \sqrtsfcc\ collider, the reference FCC-hh detector configuration has been used as a baseline~\cite{cdr_volume3, delphes_card_fcc}. For the \sqrtshelhc\, a generic detector configuration~\cite{} that aims at reproducing an average response of the HL-LHC general purpose ATLAS~\cite{} and CMS~\cite{} detectors. For the sake of conciseness, we will simply refer to the HE-LHC and the FCC detectors and will focus on the detector specifications that are relevant for measuring high \pt\ objects only. The overall contribution of pile-up is neglected altogether, as it is assumed to have a relative negligible impact of multi-TeV objects.

\subsubsection{Tracking}\label{appsub:tracking}

After collision, parton showering, hadronisation, and decays, the first step of \delphes{}is the propagation of long-lived particles inside the tracking volume within a uniform axial magnetic field parallel to the beam direction. The magnetic field strength $B$, the size of the tracking radius $L$ and the single hit spatial resolution $\sigma_{r\phi}$ are the main parameters that determine the resolution on the track transverse momentum:
\begin{equation}
\frac{\sigma(p_T)}{p_{T}} \approx \frac{\sigma_{r\phi}}{B\cdot L^2}\,.
\end{equation}
As a benchmark, we assume that the radius of the FCC inner tracking detector is $3/2$ that of the HELHC detector with a similar the magnetic field.  We also assume that the spatial resolution $\sigma_{r\phi}$ is 3 times smaller than at HELHC, which is possible by designing a more granular pixel detector~\cite{CMS:2012sda}. These specifications of the FCC detector would allow measurements of 1 TeV charged hadrons with a precision of $\sigma(p_T)/p_T  \simeq 2\%$, compared to $\sigma(p_T)/p_T \simeq 10\%$ for the HELHC detector. Central, high momentum charged hadrons tracks are assumed to be reconstructed with an efficiency $\epsilon = 95\%$.

@@

Charged particles confined inside a highly boosted jet can be extremely collimated, resulting in unresolvable tracker hits, especially in the innermost tracking layers. Although an accurate description of this feature would require a full event reconstruction by means of a GEANT-based simulation~\cite{Agostinelli:2002hh}, we constructed a simple model of this effect. A smearing on the norm and the direction of the charged particle momentum vector is applied at the stage of particle propagation. In addition, whenever two or more tracks fall within an angular separation $\sigma(\eta,\phi)$, only the highest momentum track is reconstructed. This effect can result in an additional inefficiency to that shown in Table~\ref{tab:trkeffs}, and affects tracks in the core of highly boosted jets, as shown in Figure~\ref{fig:substructure} (left).

@@

Muons are also reconstructed using tracking. Stand-alone muon is provided by the angular difference between track angle in the muon system and the radial line connection to the beam axis. Again, assuming a 2 times better position resolution of in the muon system for the FCC detector, a combined muon momentum resolution of $\sigma(p_T)/p_T  \simeq 6\%$ can be achieved for momenta as high as 10 TeV/c, as opposed to $\sigma(p_T)/p_T \simeq 6\%$ at $\pt=3~TeV$ for the HELHC detector.

@@

\subsubsection{Calorimetry and Particle-Flow}\label{appsub:calorimetry}

@@

\subsubsection{Object identification efficiencies}\label{appsub:calorimetry}

@@

A mis-tagging efficiency, that is, the probability that a particle other than $\rm{b}$ or $\rm{\tau}$ be wrongly identified as a $\rm{b}$ or a $\rm{\tau}$ has been included in the simulation and assumes a similar falling behaviour as a function of the jet momentum. For the b-tagging, the mistag efficiency are parameterised separately for light-jets (uds-quarks) and c-jets. For the $\tau-$tagging we consider only mis-identification from QCD jets.

\begin {table}[h]
\begin{center}
\begin{tabular}{ l | c | c | c | c | c }
  & electrons & muons & photons & b-jets & $\tau$-jets\\
  \hline
  \hline
HELHC & 95\% & 95\% & 95\% & (1 - \pt~[TeV]/5)$\cdot$75\% & (1 - \pt~[TeV]/5)$\cdot$60\%  \\
FCC & 99\% & 95\% & 95\%  & (1 - \pt~[TeV]/15)$\cdot$85\% & (1 - \pt~[TeV]/30)$\cdot$60\% \\
\end{tabular}
\caption{Global reconstruction efficiency of high \pt\ central objects for the HELHC and FCC detectors in Delphes.}
\label{tab:effs}
\end{center}
\end{table}

\begin {table}[h]
\begin{center}
\begin{tabular}{ l | c | c | c }
  & light (b-tag) & charm (b-tag) & QCD ($\tau$-tag)\\
  \hline
  \hline
HELHC & (1 - \pt~[TeV]/5)$\cdot$1\%  & (1 - \pt~[TeV]/5)$\cdot$10\% & (1 - \pt~[TeV]/5)$\cdot$1\%  \\
FCC & (1 - \pt~[TeV]/15)$\cdot$1\% & (1 - \pt~[TeV]/15)$\cdot$5\% & (8/9 - \pt~[TeV]/30)$\cdot$1\% \\
\end{tabular}
\caption{Mis-identification efficiency of high \pt\ central heavy flavour jets for the HELHC and FCC detectors in Delphes.}
\label{tab:effs}
\end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Treatment of the Monte-Carlo samples}
\label{subsec:mctreat}
%\subsection{Tag Rate Function}
%\label{subsec:trf}
The modelling of the backgrounds in the high tagging regimes is a challenging task. The requirement of $b$ tagging in some MC samples can drastically reduce the available statistics.
This shortage of events that pass the $b$-tagging cut in the signal regime, in conjunction with the large cross section of some of the backgrounds can lead to very spiky templates.
To overcome this problem the tag rate function (TRF) method is used. By using the TRF method, no event is cut based on its $b$-tagging count, but instead all the events are weighted.
This weight can be interpreted as the probability of the given event to contain the desired number of $b$ jets.
To achieve this, the tagging efficiency (a function of $\eta$, $\pt$ and true jet flavour) was
used to calculate the event weight based on the kinematics and flavour of the jets found in each event. More details on the method can be found in Appendix~\ref{sec:app:trf}.
Despite the fact that very large amount of Monte-Carlo statistic has been simulated in bins of $\hht$
and the usage of TRF to save events, there are still large statistical fluctuations from high weight events.
In order to reduce this effect, and when large fluctuations are observed, the background spectrum is fitted. Further details on the procedure are given in Appendix~\ref{sec:app:bgfit}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulation of the detector response}
\label{subsec:detparam}

@@

The detector response has been simulated via the Delphes software package~\cite{deFavereau:2013fsa}. For the \sqrtsfcc\ collider, the reference FCC-hh detector configuration has been used as a baseline~\cite{cdr_volume3, delphes_card_fcc}. For the \sqrtshelhc\, a generic detector configuration~\cite{} that aims at reproducing an average response of the HL-LHC general purpose ATLAS~\cite{Aad:2008zzm,Capeans:2010jnh} and CMS~\cite{Chatrchyan:2008aa} detectors. For the sake of conciseness, we will simply refer to the HE-LHC and the FCC detectors and will focus on the detector specifications that are relevant for measuring high \pt\ objects only. The overall contribution of pile-up is neglected altogether, as it is assumed to have a relative negligible impact of multi-TeV objects.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Tracking}
\label{appsub:tracking}

After collision, parton showering, hadronisation, and decays, the first step of \delphes{}is the propagation of long-lived particles inside the tracking volume within a uniform axial magnetic field parallel to the beam direction. The magnetic field strength $B$, the size of the tracking radius $L$ and the single hit spatial resolution $\sigma_{r\phi}$ are the main parameters that determine the resolution on the track transverse momentum:
\begin{equation}
\frac{\sigma(p_T)}{p_{T}} \approx \frac{\sigma_{r\phi}}{B\cdot L^2}\,.
\end{equation}
As a benchmark, we assume that the radius of the FCC inner tracking detector is $3/2$ that of the HE-LHC detector with a similar the magnetic field.  We also assume that the spatial resolution $\sigma_{r\phi}$ is 3 times smaller than at HE-LHC, which is possible by designing a more granular pixel detector~\cite{CMS:2012sda}. These specifications of the FCC detector would allow measurements of 1 TeV charged hadrons with a precision of $\sigma(p_T)/p_T  \simeq 2\%$, compared to $\sigma(p_T)/p_T \simeq 10\%$ for the HE-LHC detector. Central, high momentum charged hadrons tracks are assumed to be reconstructed with an efficiency $\epsilon = 95\%$.

@@

Charged particles confined inside a highly boosted jet can be extremely collimated, resulting in unresolvable tracker hits, especially in the innermost tracking layers. Although an accurate description of this feature would require a full event reconstruction by means of a GEANT-based simulation~\cite{Agostinelli:2002hh}, we constructed a simple model of this effect. A smearing on the norm and the direction of the charged particle momentum vector is applied at the stage of particle propagation. In addition, whenever two or more tracks fall within an angular separation $\sigma(\eta,\phi)$, only the highest momentum track is reconstructed. This effect can result in an additional inefficiency to that shown in Table~\ref{tab:trk_param}, and affects tracks in the core of highly boosted jets, as shown in Figure~\ref{fig:substructure} (left).

@@

Muons are also reconstructed using tracking. Stand-alone muon is provided by the angular difference between track angle in the muon system and the radial line connection to the beam axis. Again, assuming a 2 times better position resolution of in the muon system for the FCC detector, a combined muon momentum resolution of $\sigma(p_T)/p_T  \simeq 6\%$ can be achieved for momenta as high as 10 TeV/c, as opposed to $\sigma(p_T)/p_T \simeq 6\%$ at $\pt=3~TeV$ for the HE-LHC detector.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Calorimetry and Particle-Flow}
\label{appsub:calorimetry}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Object identification efficiencies}
\label{appsub:objid}

@@

\begin {table}[h]
\begin{center}
\begin{tabular}{ l | c | c | c | c | c }
  & electrons & muons & photons & b-jets & $\tau$-jets\\
  \hline
  \hline
HE-LHC & 95\% & 95\% & 95\% & (1 - \pt~[TeV]/5)$\cdot$75\% & (1 - \pt~[TeV]/5)$\cdot$60\%  \\
FCC & 99\% & 95\% & 95\%  & (1 - \pt~[TeV]/15)$\cdot$85\% & (1 - \pt~[TeV]/30)$\cdot$60\% \\
\end{tabular}
\caption{Global reconstruction efficiency of high \pt\ central objects for the HELHC and FCC detectors in Delphes.}
\label{tab:effs}
\end{center}
\end{table}

A mis-tagging efficiency, that is, the probability that a particle other than $\rm{b}$ or $\rm{\tau}$ be wrongly identified as a $\rm{b}$ or a $\rm{\tau}$ has been included in the simulation and assumes a similar falling behaviour as a function of the jet momentum. For the b-tagging, the mistag efficiency are parameterised separately for light-jets (uds-quarks) and c-jets. For the $\tau-$tagging we consider only mis-identification from QCD jets. Table~\ref{tab:mistag} summarises the main values for the mis-tagging efficiency.

\begin {table}[h]
\begin{center}
\begin{tabular}{ l | c | c | c }
  & light (b-tag) & charm (b-tag) & QCD ($\tau$-tag)\\
  \hline
  \hline
HE-LHC & (1 - \pt~[TeV]/5)$\cdot$1\%  & (1 - \pt~[TeV]/5)$\cdot$10\% & (1 - \pt~[TeV]/5)$\cdot$1\%  \\
FCC & (1 - \pt~[TeV]/15)$\cdot$1\% & (1 - \pt~[TeV]/15)$\cdot$5\% & (8/9 - \pt~[TeV]/30)$\cdot$1\% \\
\end{tabular}
\caption{Mis-identification efficiency of high \pt\ central heavy flavour jets for the HE-LHC and FCC detectors in Delphes.}
\label{tab:mistag}
\end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Treatment of the Monte-Carlo samples}
\label{subsec:mctreat}
%\subsection{Tag Rate Function}
%\label{subsec:trf}
The modelling of the backgrounds in the high tagging regimes is a challenging task. The requirement of $b$ tagging in some MC samples can drastically reduce the available statistics.
This shortage of events that pass the $b$-tagging cut in the signal regime, in conjunction with the large cross section of some of the backgrounds can lead to very spiky templates.
To overcome this problem the tag rate function (TRF) method is used. By using the TRF method, no event is cut based on its $b$-tagging count, but instead all the events are weighted.
This weight can be interpreted as the probability of the given event to contain the desired number of $b$ jets.
To achieve this, the tagging efficiency (a function of $\eta$, $\pt$ and true jet flavour) was
used to calculate the event weight based on the kinematics and flavour of the jets found in each event. More details on the method can be found in Appendix~\ref{sec:app:trf}.
Despite the fact that very large amount of Monte-Carlo statistic has been simulated in bins of $\hht$
and the usage of TRF to save events, there are still large statistical fluctuations from high weight events.
In order to reduce this effect, and when large fluctuations are observed, the background spectrum is fitted. Further details on the procedure are given in Appendix~\ref{sec:app:bgfit}.
